### 2023-11-06 Scripts/Manuscript/manuscript.Rmd
added the storing of the raw data as functions.

# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
# load_data(worcs_directory = "../../Data/AnalysisData")

@@

<!-- @ref(sec:measures) didn't work for section corss-reference in the paragraph above-->

@@

>>>>

# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
# load_data()

@@

<!-- @ref(sec:measures) didn't work for section cross-reference in the paragraph above-->

@@

```{r}
open_data(data = Data_ML1, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(Data_ML1))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", deparse(substitute(Data_ML1))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", deparse(substitute(Data_ML1))), ".yml")) 
```
